---
output:
  md_document:
    variant: markdown_github
    includes:
      css: README.css
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "tools/images/README-"
)
library(euler)
```

# euler

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/euler)](http://cran.r-project.org/package=euler)
[![Travis-CI Build Status](https://travis-ci.org/nathaneastwood/euler.svg?branch=master)](https://travis-ci.org/nathaneastwood/euler)
[![codecov](https://codecov.io/gh/nathaneastwood/euler/branch/master/graph/badge.svg)](https://codecov.io/gh/nathaneastwood/euler)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)

## Overview

The goal of `euler` is to offer R solutions to [Project Euler](https://projecteuler.net) problems.

## Installation

You can install the package directly from GitHub using the [`devtools` package](https://github.com/r-lib/devtools).

```{r installation, eval = FALSE}
# install.packages("devtools")
install_github("nathaneastwood/euler")
```

## Useage

We can, for example, solve [Euler problem 3](https://projecteuler.net/problem=3) using the following:

```{r euler3}
euler_3(600851475143)
```

Or we could solve [Euler problem 4](https://projecteuler.net/problem=4) using the following:

```{r euler4}
euler_4(3)
```

## Problems solved so far

This package currently offers solutions to the following Euler problems:

<details>
<summary>Click to expand</summary>

* [Problem 1](https://projecteuler.net/problem=1)
* [Problem 2](https://projecteuler.net/problem=2)
* [Problem 3](https://projecteuler.net/problem=3)
* [Problem 4](https://projecteuler.net/problem=4)
* [Problem 5](https://projecteuler.net/problem=5)
* [Problem 6](https://projecteuler.net/problem=6)
* [Problem 7](https://projecteuler.net/problem=7)
* [Problem 8](https://projecteuler.net/problem=8)
* [Problem 11](https://projecteuler.net/problem=11)
* [Problem 13](https://projecteuler.net/problem=13)
* [Problem 18](https://projecteuler.net/problem=18)
* [Problem 67](https://projecteuler.net/problem=67)
</details><break>

## Contributing

Bug reports, suggestions, and especially code contributions are welcome. Please see [CONTRIBUTING.md](https://github.com/nathaneastwood/euler/blob/master/CONTRIBUTING.md). Maintainers and contributors must follow this repository's [code of conduct](https://thoughtbot.com/open-source-code-of-conduct).
